---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# InfluentialPoints

<!-- badges: start -->
<!-- badges: end -->

The goal of InfluentialPoints is to assist users in pinpointing data points that substantially impact the model's parameters by calculating various influence metrics, including Cook's Distance, DFFITS, and Hadi's Influence Measure. It also provides visualization features, allowing users to easily spot influential points through visually engaging lollipop charts.

## Installation

You can install the development version of InfluentialPoints like so:

``` {r}
# install.packages("devtools")
library(devtools)
devtools::install_github("renswickd/R-Package-for-Influential-Points")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(InfluentialPoints)
```

```{r}
# build a lm model
model <- lm(mpg ~ wt + hp, data = mtcars)
```

```{r}
# use the function to calculate influential values and find influential points
output1 <- influential(model, type = "cooks", threshold = 0.3)
```
```{r}
# influence scores of each record in the dataset
output1$Influence_Values
```
```{r}
# influential data points in the dataset 
output1$Influential_Points
```
